Defocus Corrected Large Area Cryo-EM (DeCo-LACE) for Label-Free Detection of Molecules across Entire Cell Sections

### 2022-05-20 output/figures/matching_stat.tex
Another attempt [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/9f26f343eb6707bf20436bc0f58fa1c34dc74c00.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/9f26f343eb6707bf20436bc0f58fa1c34dc74c00/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2355455976

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{15cm} 
    \newcommand{\figheight}{3cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

\node (anchor) at (0.5,2.5) {}; 
\node[labelNode] {A};
\node[graphicNode] (panel) {\includegraphics[width=4.5cm]{content/code/img/num_matches_plot.png}};
\node (anchor) at ([shift={(0.5cm,0.0)}]panel.north east) {}; 
\node[labelNode] {B};
\node[graphicNode] (panel) {\includegraphics[width=4.5cm]{content/code/img/scores_plot.png}};
\node (anchor) at ([shift={(0.5cm,0.0)}]panel.north east) {}; 
\node[labelNode] {C};
\node[graphicNode] {\includegraphics[width=4.5cm]{content/code/img/matches_per_tile_plot.png}};
\node (anchor) at ([shift={(0.0cm,-1.0)}]0.5,2.5 |- panel.south east) {}; 
\node[labelNode] {D};
\node[graphicNode] {\includegraphics[width=14cm]{content/code/img/micrograph_with_matches.png}};
    \iftoggle{draft}{\draw[lightgray,step=1] (0,0) grid (\figwidth,\figheight);}{};
    \end{tikzpicture}
    \end{document}

>>>>

    \documentclass[tikz,border=0cm]{standalone}
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{contour}
    \contourlength{0.6pt}
    \usetikzlibrary{positioning}
    \usetikzlibrary{arrows,snakes,shapes,fadings}
    \usetikzlibrary{fit}
    \usetikzlibrary{calc}
    \def\centerarc[#1](#2)(#3:#4:#5){ \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }
    \usetikzlibrary{3d}
    \usetikzlibrary{backgrounds}
    \usepackage{fontspec}
    \setmainfont{Roboto}[
      Extension = .otf,
      UprightFont = *-Regular,
      BoldFont = *-Bold,
      ItalicFont = *-Italic,
      BoldItalicFont = *-BoldItalic,
    ]    \usepackage{etoolbox} 
    \usepackage{enumitem}
    \setlist{nosep,leftmargin=*}
    \newcommand{\figwidth}{15cm} 
    \newcommand{\figheight}{3cm} 
    \newcommand{\fontselect}{\large\bf} 
    \newcommand{\fontannot}{\bf}

@@

\node (anchor) at (0.5,2.5) {}; 
\node[labelNode] {A};
\node[graphicNode] (panel) {\includegraphics[width=4.5cm]{content/code/img/num_matches_plot.png}};
\node (anchor) at ([shift={(0.5cm,0.0)}]panel.north east) {}; 
\node[labelNode] {B};
\node[graphicNode] (panel) {\includegraphics[width=4.5cm]{content/code/img/matches_per_tile_plot.png}};
\node (anchor) at ([shift={(0.5cm,0.0)}]panel.north east) {}; 
\node[labelNode] {C};
\node[graphicNode] (panel) {\includegraphics[width=4.5cm]{content/code/img/scores_plot.png}};
\node (anchor) at ([shift={(0.0cm,-0.2)}]0.5,2.5 |- panel.south east) {}; 
\node[labelNode] {D};
\node[graphicNode] (panel) {\includegraphics[width=14cm]{content/code/img/micrograph_with_matches.png}};

\node (anchor) at ([shift={(0.0cm,-0.2)}]0.5,2.5 |- panel.south east) {}; 
\node[labelNode] {E};
\node[graphicNode] (panel) {\includegraphics[width=6cm]{content/code/img/num_matches_vs_bis.png}};

\node (anchor) at ([shift={(1.0cm,0.0)}]panel.north east) {}; 
\node[labelNode] {F};
\node[graphicNode] {\includegraphics[width=6cm]{content/code/img/snrs_vs_bis.png}};

    \iftoggle{draft}{\draw[lightgray,step=1] (0,0) grid (\figwidth,\figheight);}{};
    \end{tikzpicture}
    \end{document}
